Irt plot extra

### 2022-07-18 manuscript.Rmd
Adjust discussion and proof read the document.

Light exposure received by the eyes affects many facets of human health, well-being, and performance beyond visual sensation and perception [@boyce_light_2022]. The so-called non-image-forming (NIF) effects of light comprise light’s circadian and non-circadian influence on several physiological and psychological functions, such as the secretion of melatonin, sleep, mood, pupil size, body temperature, alertness, and higher cognitive functions [i.a. reviewed in @Bedrosian.2017;@lok2018light; @siraji2021effects; @blume_effects_2019; @paul_direct_2019; @santhi_applications_2020; @zele_editorial_2020 ].

@@

An extensive body of scientific evidence suggests that the imbalance of light and dark exposure disrupts humans’ light-dependent physiological systems [@Lunn.2017]. This, in turn, gives rise to a series of adverse health consequences, including the alteration of several hormonal rhythms, increased cancer rates, cardiovascular diseases, and metabolic disorders, such as obesity, and type II diabetes [see reviews by @Lunn.2017; @navara2007dark; @Chellappa.2019]

@@

To date, little effort has been made to understand and capture these activities. **Supplementary Table 1** summarises the existing questionnaire literature assessing light exposure-related properties. However, only a few questions of these existing tools were associated with light exposure-related behaviour. For example, the “Munich Chronotype  Questionnaire” [MCTQ; @roenneberg2003life], a popular self-report tool for identifying chronotypes via mid-sleep times, includes questions about the individual’s time spent outdoors on workdays and free days. The Visual Light Sensitivity Questionnaire-8 [@verriotto2017new] and Photosensitivity Assessment Questionnaire (PAQ; @bossini2006sensibilita), a couple of self-report tools measuring visual light sensitivity, contain single items which probe the preference for specific light situations: "In the past month, how often did you need to wear dark glasses on cloudy days or indoors?" [@verriotto2017new]; "I prefer rooms that are in semi-darkness."; [@bossini2006sensibilita]. In addition, the “Pittsburgh Sleep Quality Index” [PSQI; @buysse1989pittsburgh], a popular measure of sleep quality, contains questions about sleep and wake-up times, which are relevant to the light exposure around bedtime. 

@@

A quantitative cross-sectional fully anonymous, geographically unconstrained online survey was conducted via REDCap [@harris2009research; @harris2019redcap] by way of the University of Basel [sciCORE](https://redcap.scicore.unibas.ch). Participants were recruited via the [website](https://enlightenyourclock.org/participate-in-research) (<https://enlightenyourclock.org/participate-in-research>) of the science-communication comic book "Enlighten your clock", co-released with the survey [@Weinzaepflen.2021], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by the distribution of the survey link via f.lux [@f.lux]. The initial page of the online survey provided information about the study, including that participation was voluntary and that respondents could withdraw from participation at any time without being penalised. Subsequently, consent was recorded digitally for the adult participants (\>18 years), while under-aged participants (\<18 years) were prompted to obtain additional assent from their parents/legal guardians. Filling in all questionnaires was estimated to take less than 30 minutes, and participation was not compensated.
As a part of the demographic data, participants provided information regarding age, sex, gender identity, occupational status, COVID-19-related occupational setting, time zone/country of residence and native language. The demographic characteristics of our sample are given in **Table 1**. Participants were further asked to confirm that they participated in the survey for the first time. Additionally, five attention check items (e.g., "We want to make sure you are paying attention. What is 4+5?") were included among the questionnaires to ensure high data quality. All questions incorporating retrospective recall were aligned to a "past four weeks" period.

@@

Figure \@ref(fig:FlowchartFig) summarises the steps we followed while developing the LEBA. We conducted all analyses with the statistical software environment R [@R-base]. 
**Firstly**, we set an item pool of 48 items with a six-point Likert-type response format (0-Does not apply/I don't know, 1-Never, 2-Rarely 3-Sometimes, 4-Often, 5-Always) for our initial scale. Our purpose was to capture light exposure-related behaviour. In that context, the first two response options: "Does not apply/I don't know" and "Never" provided similar information. As such we collapsed them into one, making it a 5-point Likert-type response format (1-Never, 2-Rarely, 3-Sometimes, 4-Often, 5-Always).

**Secondly**, the two rounds of data collection were administered. 
**Thirdly**, we conducted descriptive and item analysis and proceeded to the exploratory factor analysis (EFA) using the "psych" package [@R-psych] on the data collected in the first round (EFA sample; n=`r nrow(EFA.descriptives)`), as a part of psychometric analysis. Prior to the EFA, the necessary assumptions, including sample adequacy, normality assumptions, and quality of correlation matrix, were assessed. As our data violated both the univariate and multivariate normality assumption and yielded ordinal response data, we used a polychoric correlation matrix in the EFA and employed "principal axis" (PA) as the factor extraction method [@desjardinsHandbookEducationalMeasurement2018; @watkinsStepbyStepGuideExploratory2020]. We applied a combination of methods including a Scree plot [@cattellScreeTestNumber1966], minimum average partials method [@velicerDeterminingNumberComponents1976], and Hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers. To determine the latent structure, we followed the common guidelines: (i) no factors with fewer than three items (ii) no factors with a factor loading \<0.3 (iii) no items with cross-loading \> .3 across factors [@bandalosFactorAnalysisExploratory2018]. <!-- We also conducted an EFA on non-merged response options data set (**Supplementary File 1**). -->

@@

To validate the latent structure obtained in the EFA, we conducted a categorical confirmatory factor analysis (CFA) with the weighted least squares means and variance adjusted (WLSMV) estimation [@desjardinsHandbookEducationalMeasurement2018], using the "lavaan" package [@R-lavaan] on the data collected in the second round (CFA sample; n=`r nrow(CFA.descriptives)`). We assessed the model fit using common model fit guidelines: (i) $\chi^2$ test statistics: a non-significant test statistics is required to accept the model (ii) comparative fit index (CFI) and Tucker Lewis index (TLI): close to .95 or above/ between .90-.95 and above (iii) root mean square error of approximation (RMSEA): close to .06 or below, (iv) Standardized root mean square (SRMR): close to .08 or below [@huCutoffCriteriaFit1999; @schumacker2004beginner]. However, the $\chi^2$ test is sensitive to sample size [@brownConfirmatoryFactorAnalysis2015], and SRMR does not work well with ordinal data [@RN1272]. Consequently, we judged the model fit using CFI, TLI and RMSEA.

We then assessed the measurement invariance (MI) of our scale between native English speakers (n=`r invariance.data.descriptives.count[1,2]`) and non-native English speakers (n=`r invariance.data.descriptives.count[2,2]`) in the CFA sample (n=`r nrow(CFA.descriptives)`). MI evaluates whether a construct has the psychometric equivalence and the same meaning across groups [@putnick2016measurement; @klinePrinciplesPracticeStructural2015]. We used the structural equation modelling framework applying the "lavaan" package [@R-lavaan] to assess the measurement invariance. We successively compared four nested models: configural, metric, scalar, and residual models using the $\chi^2$ difference test ($\Delta \chi^2$). Among MI models, the configural model is the least restrictive and the residual model is the most restrictive. A non-significant $\Delta \chi^2$ test between two nested measurement invariance models indicates mode fit does not significantly decrease for the superior model, thus allowing the superior invariance model to be accepted [@dimitrov2010testing; @widaman1997exploring].

**Fourthly**, as secondary analysis, we identified the educational grade level required to understand the items in our scale with the Flesch-Kincaid grade level identification method [@flesch1948new] applying the "koRpus" [@R-koRpus] package. Correspondingly, we analysed possible semantic overlap of our developed scale using the ["Semantic Scale Network" (SSN)](https://rosenbusch.shinyapps.io/semantic_net/) engine [@rosenbusch2020semantic]. The SSN detects semantically related scales and provides a cosine similarity index ranging between -.66 to 1 [@rosenbusch2020semantic]. Pairs of scales with a cosine similarity index value of 1 inidicate full semantical similarity, suggesting redundancy of the scales.

**Lastly**, we derived a short form of the LEBA employing an Item Response Theory (IRT) based analysis. We fitted each factor of the LEBA to the combined EFA and CFA sample (n=`r nrow(sem.data)`) using the graded response model [@samejima1997handbook] via the "mirt" package [@R-mirt]. IRT assesses the item quality by estimating the item discrimination, item difficulty, item information curve, and test information curve [@bakerBasicsItemResponse2017]. Item discrimination indicates how well a particular item can differentiate between participants across the given latent trait continuum ($\theta$). Item difficulty corresponds to the latent trait level at which the probability of endorsing a particular response option is 50%. The item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum. Here, we reported the item difficulty and discrimination parameter and categorize the items based on their item discrimination index: none = 0; very low = 0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high \>1.70 [@bakerBasicsItemResponse2017]. We discarded the items with a relatively flat item information curve (information \<.2) to derive the short form of LEBA. We also assessed the precision of the short LEBA utilizing the Test information curve (TIC). TIC indicates the amount of information a particular scale carries along the latent trait continuum. Additionally, the item and person fit of the fitted IRT models were analysed to gather more evidence on the validity and meaningfulness of our scale [@desjardinsHandbookEducationalMeasurement2018]. The item fit was evaluated using the RMSEA value obtained from Signed-$\chi^2$ index implementation, where an RMSEA value $\le$.06 was considered adequate item fit. The person fit was estimated employing the standardized fit index Zh statistics [@drasgow1985appropriateness]. Here, Zh \< -2 was considered as a misfit [@drasgow1985appropriateness].

@@

An expert panel comprising all authors -- researchers from chronobiology, light research, neuroscience and psychology -- developed a comprehensive item pool of 48 items. The 48 items were then examined based on their relevance and representativeness of the construct "Light Exposure Related Behaviour" by each panel member independently and modifications were suggested as required. The author team discussed the suggestions and amended the items as indicated, thus creating a 48-item scale.

@@

Participants in our survey were aged between `r min(desctable.data$slypos_demographics_age)` to `r max(desctable.data$slypos_demographics_age)` years, with an overall mean of \~ `r round(mean(desctable.data$slypos_demographics_age), 2)` years of age [Overall: `r mean(desctable.data$slypos_demographics_age)`±`r sd(desctable.data$slypos_demographics_age)`; EFA: `r mean(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1. EFA Sample"])`±`r sd(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1. EFA Sample"])`; CFA: `r mean(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2. CFA Sample"])`±`r sd(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2. CFA Sample"])`]. In total `r desc_tibble[3,2]` of the participants indicated female sex, `r desc_tibble[4,2]` indicated male and `r desc_tibble[5,2]` indicated other sex. Overall, `r desc_tibble[6,2]` participants indicated a gender-variant identity. In a "Yes/No" question regarding native language, `r desc_tibble[7,2]` of respondents [EFA: `r desc_tibble[7,3]`; CFA: `r desc_tibble[7,4]`] indicated to be native English speakers. For their "Occupational Status", more than half of the overall sample reported that they currently work, whereas `r desc_tibble[10,2]` reported that they go to school and `r desc_tibble[11,2]` responded that they do "Neither". With respect to the COVID-19 pandemic we asked participants to indicate their occupational setting during the last four weeks: In the overall sample `r desc_tibble[13,2]` of the participants indicated that they were in a home office/ home schooling setting, while `r desc_tibble[14,2]` reported face-to-face work/schooling. Lastly, `r desc_tibble[15,2]` overall reported a combination of home- and face-to-face work/schooling, whereas `r desc_tibble[16,2]`  filled in the "Neither (no work or school, or on vacation)" response option.

@@

Figure \@ref(fig:efagtPic1) and Figure \@ref(fig:efagtPic2) summarise the response patterns of our total sample (n=`r nrow(sem.data)`) for all 48 items. Most of the items appeared skewed. The Shapiro–Wilk test of univariate normality [@shapiroAnalysisVarianceTest1965] and Mardia test of multivariate normality [@mardiaMeasuresMultivariateSkewness1970] indicated our data violated both univariate and multivariate normality. The multivariate skew was `r printnum(mardia.all.data$b1p)` (p \<0.001), and the multivariate kurtosis was `r printnum(mardia.all.data$b2p)` (p \<0.001).

@@

**Supplementary Figure 1** summarises the univariate descriptive statistics for the 48 items in the EFA sample (n=`r nrow(EFA.data)`). Likewise, our data violated the univariate [@shapiroAnalysisVarianceTest1965] and multivariate normality assumptions [@mardiaMeasuresMultivariateSkewness1970]. The multivariate skew was `r printnum(mardia$b1p)` (p \<0.001) and the multivariate kurtosis yielded a value of `r printnum(mardia$b2p)` (p \<0.001). The corrected item-total correlation ranged between `r apa(low.r.corec,2,F)` -`r apa(high.r.corec,2,F)`. However, no item was discarded based on descriptive statistics or item analysis.

@@

(ref:efa-plot-print) (A) Inter-item polychoric correlation coefficients for the 48 items. 4.9 % inter-item correlation coefficients were higher than \|.30\|. 'x' denotes non-significant item-total correlation. (B) The Scree plot suggested six factors. (C) Hull method indicated that five factors were required to balance the model fit and number of parameters. (D) The histogram of nonredundant residual correlations indicated that 26% of inter-item correlations were higher than .05, hinting at a possible under-factoring.

@@

Finally, we examined the factor's interpretability in the five-factor solution and weighed it against the psychometric properties as we considered it essential to attain a balance between the two. As we deemed the five derived factors interpretable and relevant concerning our aim to capture light exposure-related behaviour, we retained all of them with 25 items for our confirmatory factor analysis (CFA), despite the apparent low reliability of the fifth factor. Two of the items showed negative factor-loading (items 44 and 21). Upon re-inspection, we recognized these items to be negatively correlated to the respective factor, and thus, we reverse-scored these two items in the CFA analysis. The internal consistency coefficient McDonald's $\omega_t$ for the total scale was `r apa(omega$omega.tot,2,T)`.

@@

Accordingly, we accept the 5-factor model with 23 items, finalizing the long Form of LEBA (see **Supplementary File 1**). The Internal consistency McDonald's $\omega_t$ coefficient for the total scale yielded `r apa(rel.k[5,6],2,F)`. Figure \@ref(fig:figcfa) depicts the obtained CFA structure, while  **Supplementary Figure 2** depicts the data distribution and endorsement pattern of the retained 23 items in our CFA sample.

@@

Our CFA sample consisted of `r mi.count[1,2]` native English speakers and `r mi.count[2,2]` non-native English speakers, whose demographic data are contrasted in **Supplementary Table 5**. As shown in Table \@ref(tab:InvarianceTab), the employed five-factor model generated acceptable fit indices over all of the fitted MI models. The model fit did not significantly decrease across the nested models implying the acceptability of the highest measurement invariance model (residual model).

@@

## Developing Short form of LEBA: IRT-Based Analysis
In order to derive a short form of the LEBA instrument, we fitted each factor of the LEBA with the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n=690). The resulting item discrimination parameters of the scale fell into categories of "very high" (10 items), "high" (4 items), "moderate" (4 items), and "low" ( 5 items), indicating a good range of discrimination along the latent trait level ($\theta$) (**Supplementary Table 6**). An examination of the item information curve (**Supplementary Figure 3**) revealed five items (1, 25, 30, 38, & 41) with relatively flat curves (I($\theta$) \<.20). We discarded those items, culminating in a short form of LEBA with five factors and 18 items (**Supplementary File 2**).

@@

Since electrical light use was globally established, people's received light exposure is not only regulated by the natural light-dark cycle but ultimately determined by their light-related behaviour, i.e. people receive different light intensities at different times depending on their light-related habits. In reviewing the literature, we found that a handful of previously introduced instruments assess aspects of light exposure by self-report (see **Supplementary Table 1**). Even fewer assessment tools have yet partially probed behavioural aspects of received light like the estimated time spent outside [MCTQ; @roenneberg2003life] or the preference for specific light situations (e.g. "I prefer rooms that are in semi-darkness."; PAQ @bossini2006sensibilita). However, none of these questionnaires systematically and thoroughly captures behaviours that modify light exposure across different lighting scenarios. Aiming to fill this gap, we have developed a self-report scale that can capture light exposure-related behaviour in multiple dimensions.

The 48 initially generated items were first applied in a geographically unconstrained quantitative cross-sectional survey, yielding responses from a large international sample (n=`r nrow(data)`).

Data collected in the first round was used to explore the latent structure (EFA sample; n=`r nrow(EFA.descriptives)`). Exploratory factor analysis revealed a five factor solution with 25 items. ("Wearing blue light filters", "Spending time outdoors", "Using phone and smartwatch in bed", "Using light before bedtime", and "Using light in the morning and during daytime"). The internal consistency reliability coefficient ordinal alpha ranged between `r apa(min(alpha.tab),2,F)`-`r apa(max(alpha.tab),2,F)`. Except for the fifth factor the internal reliability coefficients were above .70. For the fifth factor it was `r apa((alpha.tab[5,1]),2,F)`. As a rule of thumb reliability coefficient higher than .70 is considered to be satisfactory. However for scales with less than 20 items and at the early developmental stage, a value of .50 is also acceptable [@dall2010developmental; @field2013discovering; @Nunnally1978]. Also all of the factors were highly interpretable in terms of a common theme and contributed essentially towards our aim to capture light exposure related behaviour. This eventually led us to accept the obtained five-factor structure. The total scale exhibited satisfactory internal consistency (McDonald's $\omega_t$=`r apa(omega$omega.tot,2,T)`).

>>>>

Light exposure received by the eyes affects many facets of human health, well-being, and performance beyond visual sensation and perception [@boyce_light_2022]. The so-called non-image-forming (NIF) effects of light comprise light’s circadian and non-circadian influence on several physiological and psychological functions, such as the secretion of melatonin, sleep, mood, pupil size, body temperature, alertness, and higher cognitive functions [i.a. reviewed in @Bedrosian.2017;@lok2018light; @siraji2021effects; @blume_effects_2019; @paul_direct_2019; @santhi_applications_2020; @zele_editorial_2020].

@@

An extensive body of scientific evidence suggests that the imbalance of light and dark exposure disrupts humans’ light-dependent physiological systems [@Lunn.2017]. Subsequently, this disruption gives rise to a series of adverse health consequences, including the alteration of several hormonal rhythms, increased cancer rates, cardiovascular diseases, and metabolic disorders, such as obesity, and type II diabetes [see reviews by @Lunn.2017; @navara2007dark; @Chellappa.2019]

@@

To date, little effort has been made to understand and capture these activities. **Supplementary Table 1** summarises the existing questionnaire literature assessing light exposure-related properties. However, only a few questions of these existing tools were associated with light exposure-related behaviour. For example, the “Munich Chronotype  Questionnaire” [MCTQ; @roenneberg2003life], a popular self-report tool for identifying chronotypes via mid-sleep times, includes questions about the individual’s time spent outdoors on workdays and free days. The Visual Light Sensitivity Questionnaire-8 [@verriotto2017new] and Photosensitivity Assessment Questionnaire (PAQ; @bossini2006sensibilita), a couple of self-report tools measuring visual light sensitivity, contain single items which probe the preference for specific light situations: "In the past month, how often did you need to wear dark glasses on cloudy days or indoors?" [@verriotto2017new]; "I prefer rooms that are in semi-darkness."; [@bossini2006sensibilita]. In addition, the “Pittsburgh Sleep Quality Index” [PSQI; @buysse1989pittsburgh], a popular measure of sleep quality, contains questions about sleep and wake-up times, which are relevant to light exposure around bedtime. 

@@

A quantitative cross-sectional, fully anonymous, geographically unconstrained online survey was conducted via REDCap [@harris2009research; @harris2019redcap] by way of the University of Basel [sciCORE](https://redcap.scicore.unibas.ch). Participants were recruited via the [website](https://enlightenyourclock.org/participate-in-research) (<https://enlightenyourclock.org/participate-in-research>) of the science-communication comic book "Enlighten your clock", co-released with the survey [@Weinzaepflen.2021], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by the distribution of the survey link via f.lux [@f.lux]. The initial page of the online survey provided information about the study, including that participation was voluntary and that respondents could withdraw from participation at any time without being penalised. Subsequently, consent was recorded digitally for the adult participants (\>18 years), while under-aged participants (\<18 years) were prompted to obtain additional assent from their parents/legal guardians. Filling in all questionnaires was estimated to take less than 30 minutes, and participation was not compensated.
As a part of the demographic data, participants provided information regarding age, sex, gender identity, occupational status, COVID-19-related occupational setting, time zone/country of residence and native language. The demographic characteristics of our sample are given in **Table 1**. Participants were further asked to confirm that they participated in the survey for the first time. Additionally, five attention check items (e.g., "We want to make sure you are paying attention. What is 4+5?") were included among the questionnaires to ensure high data quality. All questions incorporating retrospective recall were aligned to a "past four weeks" period.

@@

Figure \@ref(fig:FlowchartFig) summarises the steps we followed while developing the LEBA. We conducted all analyses with the statistical software environment R [@R-base]. 
**Firstly**, we set an item pool of 48 items with a six-point Likert-type response format (0-Does not apply/I don't know, 1-Never, 2-Rarely 3-Sometimes, 4-Often, 5-Always) for our initial scale. Our purpose was to capture light exposure-related behaviour. In that context, the first two response options: "Does not apply/I don't know" and "Never", provided similar information. As such, we collapsed them into one, making it a 5-point Likert-type response format (1-Never, 2-Rarely, 3-Sometimes, 4-Often, 5-Always).

**Secondly**, the two rounds of data collection were administered. 
**Thirdly**, we conducted descriptive and item analysis and proceeded to the exploratory factor analysis (EFA) using the "psych" package [@R-psych] on the data collected in the first round (EFA sample; n=`r nrow(EFA.descriptives)`), as a part of psychometric analysis. Prior to the EFA, the necessary assumptions, including sample adequacy, normality assumptions, and quality of correlation matrix, were assessed. As our data violated both the univariate and multivariate normality assumption and yielded ordinal response data, we used a polychoric correlation matrix in the EFA and employed "principal axis" (PA) as the factor extraction method [@desjardinsHandbookEducationalMeasurement2018; @watkinsStepbyStepGuideExploratory2020]. We applied a combination of methods, including a Scree plot [@cattellScreeTestNumber1966], minimum average partials method [@velicerDeterminingNumberComponents1976], and Hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers. To determine the latent structure, we followed the common guidelines: (i) no factors with fewer than three items (ii) no factors with a factor loading \<0.3 (iii) no items with cross-loading \> .3 across factors [@bandalosFactorAnalysisExploratory2018]. <!-- We also conducted an EFA on the non-merged response options data set (**Supplementary File 1**). -->

@@

To validate the latent structure obtained in the EFA, we conducted a categorical confirmatory factor analysis (CFA) with the weighted least squares means and variance adjusted (WLSMV) estimation [@desjardinsHandbookEducationalMeasurement2018], using the "lavaan" package [@R-lavaan] on the data collected in the second round (CFA sample; n=`r nrow(CFA.descriptives)`). We assessed the model fit using standard model fit guidelines: (i) $\chi^2$ test statistics: a non-significant test statistics is required to accept the model (ii) comparative fit index (CFI) and Tucker Lewis index (TLI): close to .95 or above/ between .90-.95 and above (iii) root mean square error of approximation (RMSEA): close to .06 or below, (iv) Standardized root mean square (SRMR): close to .08 or below [@huCutoffCriteriaFit1999; @schumacker2004beginner]. However, the $\chi^2$ test is sensitive to sample size [@brownConfirmatoryFactorAnalysis2015], and SRMR does not work well with ordinal data [@RN1272]. Consequently, we judged the model fit using CFI, TLI and RMSEA.

We then assessed the measurement invariance (MI) of our scale between native English speakers (n=`r invariance.data.descriptives.count[1,2]`) and non-native English speakers (n=`r invariance.data.descriptives.count[2,2]`) in the CFA sample (n=`r nrow(CFA.descriptives)`). MI evaluates whether a construct has the psychometric equivalence and the same meaning across groups [@putnick2016measurement; @klinePrinciplesPracticeStructural2015]. We used the structural equation modelling framework applying the "lavaan" package [@R-lavaan] to assess the measurement invariance. We successively compared four nested models: configural, metric, scalar, and residual models using the $\chi^2$ difference test ($\Delta \chi^2$). Among MI models, the configural model is the least restrictive, and the residual model is the most restrictive. A non-significant $\Delta \chi^2$ test between two nested measurement invariance models indicates mode fit does not significantly decrease for the superior model, thus allowing the superior invariance model to be accepted [@dimitrov2010testing; @widaman1997exploring].

**Fourthly**, as secondary analysis, we identified the educational grade level required to understand the items in our scale with the Flesch-Kincaid grade level identification method [@flesch1948new] applying the "koRpus" [@R-koRpus] package. Correspondingly, we analysed possible semantic overlap of our developed scale using the ["Semantic Scale Network" (SSN)](https://rosenbusch.shinyapps.io/semantic_net/) engine [@rosenbusch2020semantic]. The SSN detects semantically related scales and provides a cosine similarity index ranging between -.66 to 1 [@rosenbusch2020semantic]. Pairs of scales with a cosine similarity index value of 1 inidicate full semantical similarity, suggesting redundancy.

**Lastly**, we derived a short form of the LEBA employing an Item Response Theory (IRT) based analysis. We fitted each factor of the LEBA to the combined EFA and CFA sample (n=`r nrow(sem.data)`) using the graded response model [@samejima1997handbook] via the "mirt" package [@R-mirt]. IRT assesses the item quality by estimating the item discrimination, item difficulty, item information curve, and test information curve [@bakerBasicsItemResponse2017]. Item discrimination indicates how well a particular item can differentiate between participants across the given latent trait continuum ($\theta$). Item difficulty corresponds to the latent trait level at which the probability of endorsing a particular response option is 50%. The item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum. Here, we reported the item difficulty and discrimination parameter and categorize the items based on their item discrimination index: none = 0; very low = 0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high \>1.70 [@bakerBasicsItemResponse2017]. We discarded the items with a relatively flat item information curve (information \<.2) to derive the short form of LEBA. We also assessed the precision of the short LEBA utilizing the Test information curve (TIC). TIC indicates the amount of information a particular scale carries along the latent trait continuum. Additionally, the item and person fit of the fitted IRT models were analysed to gather more evidence on the validity and meaningfulness of our scale [@desjardinsHandbookEducationalMeasurement2018]. The item fit was evaluated using the RMSEA value obtained from Signed-$\chi^2$ index implementation, where an RMSEA value $\le$.06 was considered an adequate item fit. The person fit was estimated employing the standardized fit index Zh statistics [@drasgow1985appropriateness]. Here, Zh \< -2 was considered as a misfit [@drasgow1985appropriateness].

@@

An expert panel comprising all authors -- researchers from chronobiology, light research, neuroscience and psychology -- developed a comprehensive item pool of 48 items. The 48 items were examined independently based on their relevance and representativeness of the construct "Light Exposure Related Behaviour" by each panel member, and modifications were suggested as required. The author team discussed the suggestions and amended the items as indicated, thus creating a 48-item scale.

@@

Participants in our survey were aged between `r min(desctable.data$slypos_demographics_age)` to `r max(desctable.data$slypos_demographics_age)` years, with an overall mean of \~ `r round(mean(desctable.data$slypos_demographics_age), 2)` years of age [Overall: `r mean(desctable.data$slypos_demographics_age)`±`r sd(desctable.data$slypos_demographics_age)`; EFA: `r mean(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1. EFA Sample"])`±`r sd(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1. EFA Sample"])`; CFA: `r mean(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2. CFA Sample"])`±`r sd(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2. CFA Sample"])`]. In total, `r desc_tibble[3,2]` of the participants indicated female sex, `r desc_tibble[4,2]` indicated male, and `r desc_tibble[5,2]` indicated other sex. Overall, `r desc_tibble[6,2]` participants reported a gender-variant identity. In a "Yes/No" question regarding native language, `r desc_tibble[7,2]` of respondents [EFA: `r desc_tibble[7,3]`; CFA: `r desc_tibble[7,4]`] indicated to be native English speakers. For their "Occupational Status", more than half of the overall sample reported that they currently work, whereas `r desc_tibble[10,2]` reported that they go to school, and `r desc_tibble[11,2]` responded that they do "Neither". With respect to the COVID-19 pandemic, we asked participants to indicate their occupational setting during the last four weeks: In the overall sample `r desc_tibble[13,2]` of the participants indicated that they were in a home office/ home schooling setting, while `r desc_tibble[14,2]` reported face-to-face work/schooling. Lastly, `r desc_tibble[15,2]` overall reported a combination of home- and face-to-face work/schooling, whereas `r desc_tibble[16,2]`  filled in the "Neither (no work or school, or on vacation)" response option.

@@

Figure \@ref(fig:efagtPic1) and Figure \@ref(fig:efagtPic2) summarise the response patterns of our total sample (n=`r nrow(sem.data)`) for all 48 items. Most of the items appeared skewed. The Shapiro–Wilk test of univariate normality [@shapiroAnalysisVarianceTest1965] and Mardia test of multivariate normality [@mardiaMeasuresMultivariateSkewness1970] indicated that our data violated both univariate and multivariate normality. The multivariate skew was `r printnum(mardia.all.data$b1p)` (p \<0.001), and the multivariate kurtosis was `r printnum(mardia.all.data$b2p)` (p \<0.001).

@@

**Supplementary Figure 1** summarises the univariate descriptive statistics for the 48 items in the EFA sample (n=`r nrow(EFA.data)`). Likewise, our data violated the univariate [@shapiroAnalysisVarianceTest1965] and multivariate normality assumptions [@mardiaMeasuresMultivariateSkewness1970]. The multivariate skew was `r printnum(mardia$b1p)` (p \<0.001) and the multivariate kurtosis yielded a value of `r printnum(mardia$b2p)` (p \<0.001). The corrected item-total correlation ranged between `r apa(low.r.corec,2,F)` and `r apa(high.r.corec,2,F)`. However, no item was discarded based on descriptive statistics or item analysis.

@@

(ref:efa-plot-print) (A) Inter-item polychoric correlation coefficients for the 48 items. 4.9 % inter-item correlation coefficients were higher than \|.30\|. 'x' denotes a non-significant item-total correlation. (B) The Scree plot suggested six factors. (C) Hull method indicated that five factors were required to balance the model fit and number of parameters. (D) The histogram of nonredundant residual correlations indicated that 26% of inter-item correlations were higher than .05, hinting at a possible under-factoring.

@@

Lastly, we examined the factor's interpretability in the five-factor solution and weighed it against the psychometric properties as we considered it essential to attain a balance between the two. As we deemed the five derived factors interpretable and relevant concerning our aim to capture light exposure-related behaviour, we retained all of them with 25 items for our confirmatory factor analysis (CFA), despite the apparent lower reliability of the fifth factor. Two of the items showed negative factor-loading (items 44 and 21). Upon re-inspection, we recognized these items to be negatively correlated to the respective factor, and thus, we reverse-scored these two items in the CFA analysis. The internal consistency coefficient McDonald's $\omega_t$ for the total scale was `r apa(omega$omega.tot,2,T)`.

@@

Accordingly, we accept the five-factor model with 23 items, finalizing the long Form of LEBA (see **Supplementary File 1**). The Internal consistency McDonald's $\omega_t$ coefficient for the total scale yielded `r apa(rel.k[5,6],2,F)`. Figure \@ref(fig:figcfa) depicts the obtained CFA structure, while  **Supplementary Figure 2** depicts the data distribution and endorsement pattern of the retained 23 items in our CFA sample.

@@

Our CFA sample consisted of `r mi.count[1,2]` native English speakers and `r mi.count[2,2]` non-native English speakers, whose demographic data are contrasted in **Supplementary Table 5**. As shown in Table \@ref(tab:InvarianceTab), the employed five-factor model generated acceptable fit indices over all of the fitted MI models. The model fit did not significantly decrease across the nested models, implying the acceptability of the highest measurement invariance model (residual model).

@@

## Developing a Short Form of LEBA: IRT-Based Analysis
In order to derive a short form of the LEBA instrument, we fitted each factor of the LEBA with the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n=690). The resulting item discrimination parameters of the scale fell into categories of "very high" (10 items), "high" (4 items), "moderate" (4 items), and "low" ( 5 items), indicating a good range of discrimination along the latent trait level ($\theta$) (**Supplementary Table 6**). An examination of the item information curve (**Supplementary Figure 3**) revealed five items (1, 25, 30, 38, & 41) with relatively flat curves (I($\theta$) \<.20). We discarded those items, culminating in a short form of LEBA with five factors and 18 items (**Supplementary File 2**).

@@

Nowadays, in many industrialized countries, most of the time is spent in enclosed buildings [@Klepeis.2001], where people's received light is determined not only by the natural light-dark cycle but by exposure to artificial light sources. Accordingly, people receive varying light intensities at different times, ultimately depending on their light-related behavioural habits. As established by extensive evidence, the timing, duration and intensity of light exposure, among other light properties, affect many aspects of human health, well-being, and performance [i.a. reviewed in @Bedrosian.2017;@lok2018light; @siraji2021effects; @blume_effects_2019; @paul_direct_2019; @santhi_applications_2020; @zele_editorial_2020]. Thus, there is a clear need for guidance [see @Brown.2022] and assessment regarding healthy light exposure and consequentially healthy light-related behaviour. 
In reviewing the literature, we found that a handful of previously introduced instruments assess aspects of light exposure by self-report (see **Supplementary Table 1**). Even fewer assessment tools have yet partially probed behavioural aspects of received light like the estimated time spent outside [MCTQ; @roenneberg2003life] or the preference for specific light situations (e.g. "I prefer rooms that are in semi-darkness."; PAQ @bossini2006sensibilita). However, none of these questionnaires systematically and thoroughly captures behaviours that modify light exposure across different lighting scenarios. With the present LEBA tool, we have developed two versions of a self-report scale that can capture light exposure-related behaviour in multiple dimensions.

The 48 initially generated items were applied in a large-scale geographically unconstrained cross-sectional survey, yielding (n=`r nrow(data)`) complete datasets. Moreover, to assure high data quality, this included only data where the five “attention check items” throughout the survey were passed. As a result, data was recorded from `r nrow(num.countries)` countries and `r nrow(numUTC)` time zones, including native and non-native English speakers from a sex-balanced and age-diverse sample (see Table 1). The acquired study population complied with our objective to avoid bias from a selective sample, which is crucial when relying on voluntary uncompensated participation.

Data collected in the first round was used to explore the latent structure (EFA sample; n=`r nrow(EFA.descriptives)`). The exploratory factor analysis revealed a highly interpretable five-factor solution ("Wearing blue light filters", "Spending time outdoors", "Using phone and smartwatch in bed", "Using light before bedtime", and "Using light in the morning and during daytime") with 25 items. The total scale exhibited satisfactory internal consistency (McDonald's $\omega_t$=`r apa(omega$omega.tot,2,T)`).
